---
title: "Statistical Inference Week 3 Lecture"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
##Confidence Interval
####Simulation of T distribution(8-01)
```{r}
k <- 1000
xvals <- seq(-5, 5, length = k)
library(ggplot2)
myplot <- function(df){  
    d <- data.frame(y = c(dnorm(xvals), dt(xvals, df)),                  
                    x = xvals,                  
                    dist = factor(rep(c("Normal", "T"), c(k,k))))  
    g <- ggplot(d, aes(x = x, y = y))   
    g <- g + geom_line(size = 2, aes(colour = dist))
    g
}
library(manipulate)
manipulate(myplot(mu), mu = slider(1, 20, step = 1))
```
T distribution has heavier tail

```{r}
pvals <- seq(.5, .99, by = .01)
myplot2 <- function(df){  
    d <- data.frame(n= qnorm(pvals),t=qt(pvals, df),                  
                    p = pvals)  
    g <- ggplot(d, aes(x= n, y = t))  
    g <- g + geom_abline(size = 2, col = "lightblue")  
    g <- g + geom_line(size = 2, col = "black")  
    g <- g + geom_vline(xintercept = qnorm(0.975))  
    g <- g + geom_hline(yintercept = qt(0.975, df))
    g
}
manipulate(myplot2(df), df = slider(1, 20, step = 1))
```
#####Note's sbout the t interval 
-Paired observation are often analyzed using the t interval by taking deffirences
-As n becomes larger,converges to standard normal quantiles;interval converges to the same    ??????interval as the CLT yeilded
-For skweed distribution, t interval assumptionins are violated,no sense a lot to make            interval

###08-02;Confidencec Interval example
####Sleep data
```{r}
library(datasets)
data(sleep)
head(sleep)
```
```{r}
g1 <- sleep$extra[1 : 10]; g2 <- sleep$extra[11 : 20]
difference <- g2 - g1
mn <- mean(difference); s <- sd(difference); n <- 10
mn + c(-1, 1) * qt(.975, n-1) * s / sqrt(n)
t.test(difference) ##Simply perferm test with generating confidence interval
t.test(g2, g1, paired = TRUE)  ##or using paired funtion; doing the exactly the same thing without take difference in the sample beoforehand
t.test(extra ~ I(relevel(group, 2)), paired = TRUE, data = sleep)
```

###08-03;Independent group T intervals
-Suppose that we want to copare the mean blood pressure between two groups in a randamized    trial;those who received the treatment to those sho received a placebo

-We canonot use the paired t test bcuz the groups are independent and may have different      sample sizes

-We now present methods for comparing independent groups

####Example(Pooled SD)
```{r}
sp <- sqrt((7 * 15.34^2 + 20 * 18.23^2) / (8 + 21 - 2)) ##Pooled satandard deviation
#if the samle sizes from group X and group Y is the same, pooled standard deviation is just a mean of the variance from the X groups and the variance from the Y group
132.86 - 127.44 + c(-1, 1) * qt(.975, 27) * sp * (1 / 8 + 1 / 21)^.5
```
includes ZERO

####Mistakenly treating the sleep data as grouped
```{r}
data(sleep)
x1 <- sleep$extra[sleep$group == 1]
x2 <- sleep$extra[sleep$group == 2]
n1 <- length(g1); n2 <- length(g2)
sp <- sqrt( ((n1 - 1) * sd(x1)^2 + (n2-1) * sd(x2)^2) / (n1 + n2-2))
md <- mean(g2) - mean(g1)
semd <- sp * sqrt(1 / n1 + 1/n2)
rbind(md + c(-1, 1) * qt(.975, n1 + n2 - 2) * semd,  
t.test(g2, g1, paired = FALSE, var.equal = TRUE)$conf,
t.test(g2, g1, paired = TRUE)$conf  ##$conf=derive confidence interval
)
```

```{r}
library(datasets); data(ChickWeight); library(reshape2)
##define weight gain or loss
wideCW <- dcast(ChickWeight, Diet + Chick ~ Time, value.var = "weight")
names(wideCW)[-(1 : 2)] <- paste("time", names(wideCW)[-(1 : 2)], sep = "")
library(dplyr)
wideCW <- mutate(wideCW, 
                 gain = time21 - time0
)
```

####Interval
```{r}
wideCW14 <- subset(wideCW, Diet %in% c(1, 4)) ##Extract observation bsed on the categoloy of diet 1 and diet 4
rbind(
    t.test(gain ~ Diet, paired = FALSE, var.equal = TRUE, data = wideCW14)$conf,  ###vae.equal=if variance is constant or not
    t.test(gain ~ Diet, paired = FALSE, var.equal = FALSE, data = wideCW14)$conf
)
```

###08-04;Unequal Variance
In the case of unequal variance form independt groups, can do some arrangement in DOF
In R ;t.test(....,var.equal=FALSE)


##Hypothesis testing
###09-01;Hypothesis testing
#####Exmaple
-Suppose that in a sample of 100 overweight subjects with other risl factors for sleep        disordered breathing at a sleep clinic,the mean RDI was 32 events/hour with a standard       deviation of 10 events/hour
            H0;mu=30
            H1;mu>30
            where mu is population mean
            
###09-02;Example of choosing a rejection region
####Ex.cont
SD=10/sqrt(100)=1
H0;Xbar~N(30,1)
We want ot choose C so that P(Xbar>C;H0) is 5%
The 95th percentile of a normal distribution is 1.645 standard deviations form the mean
If C=30+1*1.645=31.645
   -Then the probability that a N(30,1) is lager that it is 5%
   -So the rule "Reject H0 when Xbar>=31.645" has the property that the probability of rejection is 5% if H0 is true
   
###09-03; T test
Consider our exmaple again. Suppose that n=16

        (Xbar-30)/{s/sqrt(16)}      follows a Tdist with 15 under H0
        
-The 95th percentile of the T dist with 15 df is 1.7531(R; qt(95,15))

####Two sided tests
H0;mu=/30
-We want the probability of rejecting under thenull to be 5%, split equally as 2.5% in the    upper tail and 25% in the lower tail

- qt(.975,15);qt(.0.25,15)

###09-04; Two group testing
use t.test
```{r}
library(UsingR);data(father.son)
t.test(father.son$sheight-father.son$fheight)
```
We have 1077 pairs that we took difference
n is large, distinction of z and t is irrelevant here

####Two group interval
-Test H0;mu1=mu2
```{r}
library(datasets); data(ChickWeight); library(reshape2)
##define weight gain or loss
wideCW <- dcast(ChickWeight, Diet + Chick ~ Time, value.var = "weight")
names(wideCW)[-(1 : 2)] <- paste("time", names(wideCW)[-(1 : 2)], sep="")
library(dplyr)
wideCW <- mutate(wideCW,  
                 gain = time21 - time0
)
wideCW14 <- subset(wideCW, Diet %in% c(1, 4))
t.test(gain ~ Diet, paired = FALSE,       ##Predictor is follwing ~  ##Pair is false since diet1 has nothing to do with diet4 in here
       var.equal = TRUE, data = wideCW14)
```

##Pvalues
###10-01;P-values
Suppose that you get a T stats of 2.5 for 15 dof testing H0;mu=mu0 vs H1; mu>mu0
    - What's the probability of getting a Tstats as large as 2.5
    ```{r}
pt(2.5,15,lower.tail = FALSE)
    ```
###10-02;Pvalue further examples
Suppose that a friend has 8 kids, 7 of which are girls and mone twis

If each gender has an independent 50% of probability for each birth, what's the probability    of getting 7 or more girls out of 8 births

    H0;p=0.5 vs H1;p>0.5
    
```{r}
choose(8,7)*0.5^8+choose(8,8)*0.5^8


pbinom(6,size=8,prob = 0.5,lower.tail = FALSE)
```

####Poisson example
SUppose that a hospital has an infection rate of 10 infections per 100 person/days at         risk(rate of 0.1) during the last mornitaring period

Assume that an infection rate of 0.05 is an important benchmark(eg.if it is above that         hospital has to do some quality control etc..)

Givent the model, could the observed rate being larger than 0.05 be attributed to chance?

Under H0;lambda=0.05 so that lambda(0)100=5

Consider H1:lambda>0.05

Question here is that what's the probability of observing 10 or more infections
```{r}
ppois(9, 5, lower.tail = FALSE)
```