---
title: "Statistical Inference Week 3 Lecture"
output: html_notebook
---
##Confidence Interval
####Simulation of T distribution(8-01)
```{r}
k <- 1000
xvals <- seq(-5, 5, length = k)
library(ggplot2)
myplot <- function(df){  
    d <- data.frame(y = c(dnorm(xvals), dt(xvals, df)),                  
                    x = xvals,                  
                    dist = factor(rep(c("Normal", "T"), c(k,k))))  
    g <- ggplot(d, aes(x = x, y = y))   
    g <- g + geom_line(size = 2, aes(colour = dist))
    g
}
library(manipulate)
manipulate(myplot(mu), mu = slider(1, 20, step = 1))
```
T distribution has heavier tail

```{r}
pvals <- seq(.5, .99, by = .01)
myplot2 <- function(df){  
    d <- data.frame(n= qnorm(pvals),t=qt(pvals, df),                  
                    p = pvals)  
    g <- ggplot(d, aes(x= n, y = t))  
    g <- g + geom_abline(size = 2, col = "lightblue")  
    g <- g + geom_line(size = 2, col = "black")  
    g <- g + geom_vline(xintercept = qnorm(0.975))  
    g <- g + geom_hline(yintercept = qt(0.975, df))
    g
}
manipulate(myplot2(df), df = slider(1, 20, step = 1))
```
#####Note's sbout the t interval 
-Paired observation are often analyzed using the t interval by taking deffirences
-As n becomes larger,converges to standard normal quantiles;interval converges to the same    ??????interval as the CLT yeilded
-For skweed distribution, t interval assumptionins are violated,no sense a lot to make            interval

###08-02;Confidencec Interval example
####Sleep data
```{r}
library(datasets)
data(sleep)
head(sleep)
```
```{r}
g1 <- sleep$extra[1 : 10]; g2 <- sleep$extra[11 : 20]
difference <- g2 - g1
mn <- mean(difference); s <- sd(difference); n <- 10
mn + c(-1, 1) * qt(.975, n-1) * s / sqrt(n)
t.test(difference) ##Simply perferm test with generating confidence interval
t.test(g2, g1, paired = TRUE)  ##or using paired funtion; doing the exactly the same thing without take difference in the sample beoforehand
t.test(extra ~ I(relevel(group, 2)), paired = TRUE, data = sleep)
```

###08-03;Independent group T intervals
-Suppose that we want to copare the mean blood pressure between two groups in a randamized    trial;those who received the treatment to those sho received a placebo

-We canonot use the paired t test bcuz the groups are independent and may have different      sample sizes

-We now present methods for comparing independent groups

####Example(Pooled SD)
```{r}
sp <- sqrt((7 * 15.34^2 + 20 * 18.23^2) / (8 + 21 - 2)) ##Pooled satandard deviation
#if the samle sizes from group X and group Y is the same, pooled standard deviation is just a mean of the variance from the X groups and the variance from the Y group
132.86 - 127.44 + c(-1, 1) * qt(.975, 27) * sp * (1 / 8 + 1 / 21)^.5
```
includes ZERO

####Mistakenly treating the sleep data as grouped
```{r}
data(sleep)
x1 <- sleep$extra[sleep$group == 1]
x2 <- sleep$extra[sleep$group == 2]
n1 <- length(g1); n2 <- length(g2)
sp <- sqrt( ((n1 - 1) * sd(x1)^2 + (n2-1) * sd(x2)^2) / (n1 + n2-2))
md <- mean(g2) - mean(g1)
semd <- sp * sqrt(1 / n1 + 1/n2)
rbind(md + c(-1, 1) * qt(.975, n1 + n2 - 2) * semd,  
t.test(g2, g1, paired = FALSE, var.equal = TRUE)$conf,
t.test(g2, g1, paired = TRUE)$conf  ##$conf=derive confidence interval
)
```

```{r}
library(datasets); data(ChickWeight); library(reshape2)
##define weight gain or loss
wideCW <- dcast(ChickWeight, Diet + Chick ~ Time, value.var = "weight")
names(wideCW)[-(1 : 2)] <- paste("time", names(wideCW)[-(1 : 2)], sep = "")
library(dplyr)
wideCW <- mutate(wideCW, 
                 gain = time21 - time0
)
```

####INterval
```{r}
wideCW14 <- subset(wideCW, Diet %in% c(1, 4)) ##Extract observation bsed on the categoloy of diet 1 and diet 4
rbind(
    t.test(gain ~ Diet, paired = FALSE, var.equal = TRUE, data = wideCW14)$conf,  ###vae.equal=if variance is constant or not
    t.test(gain ~ Diet, paired = FALSE, var.equal = FALSE, data = wideCW14)$conf
)
```

###08-04;Unequal Variance
In the case of unequal variance form independt groups, can do some arrangement in DOF
In R ;t.test(....,var.equal=FALSE)


##Hypothesis testing
###09-01;Hypothesis testing
