---
title: "Statistical Inference Week2 Quiz"
output: html_notebook
---

###Q1
####What is the variance of the distribution of the average an IID draw of nn observations from a population with mean mu and variance sigma^2?
CLT

###Q2
####Suppose that diastolic blood pressures (DBPs) for men aged 35-44 are normally distributed with a mean of 80 (mm Hg) and a standard deviation of 10. About what is the probability that a random 35-44 year old has a DBP less than 70?
```{r}
print(pnorm(70,mean=80,sd=10))
```

###Q3
####Brain volume for adult women is normally distributed with a mean of about 1,100 cc for women with a standard deviation of 75 cc. What brain volume represents the 95th percentile?
```{r}
print(qnorm(.95,mean=1100,sd=75))
```
###Q4
####Refer to the previous question. Brain volume for adult women is about 1,100 cc for women with a standard deviation of 75 cc. Consider the sample mean of 100 random adult women from this population. What is the 95th percentile of the distribution of that sample mean?
```{r}
print(qnorm(.95,mean=1100,sd=75/sqrt(100)))
```

###Q5
####You flip a fair coin 5 times, about what's the probability of getting 4 or 5 heads?
```{r}
print(choose(5,4)*.5^5+choose(5,5)*.5^5)
```

###Q6
####The respiratory disturbance index (RDI), a measure of sleep disturbance, for a specific population has a mean of 15 (sleep events per hour) and a standard deviation of 10. They are not normally distributed. Give your best estimate of the probability that a sample mean RDI of 100 people is between 14 and 16 events per hour?
```{r}
mean<-15
sd<-10
print(error<-10/sqrt(100))
```
Application of CLT, even though data is not normally distributed, the distribution of mean of samples is very similar to normally distributed. Standard error is 1, 14-16 is within 1 standard error range from the mean. 

###Q7
####Consider a standard uniform density. The mean for this density is .5 and the variance is 1 / 12. You sample 1,000 observations from this distribution and take the sample mean, what value would you expect it to be near?

close to .5

###Q8
####The number of people showing up at a bus stop is assumed to be

####Poisson with a mean of 5 5 people per hour. You watch the bus

####stop for 3 hours. About what's the probability of viewing 10 or fewer people?
```{r}
print(ppois(10,lambda=5*3))
```