---
title: "Statistical Inference Week2"
output: html_notebook
---

#Variability

##Standard error of the mean

###Simulation example
Standard normals have variance1; means of n standard normanls have standard deviation 1/sqr(n)
```{r}
nosim<-1000
n<-10
sd(apply(matrix(rnorm(nosim*n),nosim),1,mean))

1/sqrt(n)
```
Standar uniforms have variance 1/12,means of random samples of n uniforms have sd 1/sqrt(12*n)
```{r}
nosim<-1000
n<-10
sd(apply(matrix(runif(nosim*n),nosim),1,mean))
#ten uniforms,take thier aveages,And do that over and over again
#And then take the standars deviation of the collection of averages of ten uniforms,and that will tell us about the distribution of averages of ten uniforms from this population

1/sqrt(12*n)
```

Poisson(4) has variance 4;means of random samples of n Poisson(4) have sd 2/sqrt(n)
```{r}
nosim<-1000
n<-10
sd(apply(matrix(rpois(nosim*n,4),nosim),1,mean))

2/sqrt(n)
```

Fair coin flips have variance 0.25,means of random sample of n coin flips have sd 1/(s/sqrt(n))
```{r}
nosim<-1000
n<-10
sd(apply(matrix(sample(0:1,nosim*n,replace=TRUE),nosim),1,mean))

1/(2*sqrt(n))
```

##Variance data example
```{r}
library(UsingR); data(father.son); 
x <- father.son$sheight
n<-length(x)
round(c(var(x),var(x)/n,sd(x)/sqrt(n)),2)
```

#Distribution

##Biominal distribution
As general idea of this distribution the trials where only two outcomes happen as results like coin flips, such kind of trials follow Binomial distribution

Suppose a friend have 7 girls sister
Wha is probability of getting 7or more girls out of 8 givent that the probability of each gender birth is .5
```{r}
choose(8,7)*.5^8+choose(8,8)*.5^8

pbinom(6, size = 8, prob = 0.5, lower.tail = FALSE)
```

##The normal distribution
Gaussian distibution with mean mu and variance sigma^2
        
        #X~N(mu,sigma^2)
        

Question; What is the 95th percentile of a N(mu,sigma^2) distribution?
```{r}
qnorm(.95,mean=1,sd=1)
1+1.645

```

Question; What is the prbability that a N(mu,sigma^2)RV is larger than x?
```{r}
1-qnorm(.95,mean=1,sd=1)
```

Example
Assume that the number of daily ad clicks for a compant is roughly normally distributed with a mean of 1020 and a standard deviation of 50. What's the probability of getting more than 1,160 clicks in a day?

Point; (1160-1020)/50=28, almost 3 sd units, then somewhere around 97~98%
```{r}
pnorm(1160,mean=1020,sd=50,lower.tail = FALSE)

pnorm(2.8,lower.tail = FALSE)
```
Exmple
Assume that the number of daily ad clicks for a compant is roughly normally distributed with a mean of 1020 and a standard deviation of 50. What number of daily ad clicks would represent the one where 75% of days have fewer clicks(assuming days are independent and identically distributed)?
```{r}
qnorm(.75,mean=1020,sd=50)
```

##Poisson
Example 
The number of people that show up at a bus stop is Posisson with a mean of 2.5 per hour.
If watching the bus stop for 4hours, what is the probability that 3 or fewer peoplr show up for the whole time.

```{r}
ppois(3,lambda=2.5*4)
```
Example;Poisson approximation to the binomial
We flip a coin with success probability 0.01 five hundred times
What's the probability of 2 or fewer successes?
```{r}
pbinom(2,size=500,prob=0.01)

ppois(2,lambda = 500*0.01)
```

#Asymptotics

##Law of Large numbers in action
Example
```{r}
n<-1000
means<-cumsum(rnorm(n))/(1:n)
library(ggplot2)
g <- ggplot(data.frame(x = 1:n, y = means), aes(x = x, y = y))
g <- g + geom_hline(yintercept = 0) + geom_line(size = 2)
g <- g + labs(x = "Number of obs", y = "Cumulative mean")
g
```
As time goes on the results starts to converge to the mean of zero

Example with coin flip
```{r}
means <- cumsum(sample(0:1, n, replace = TRUE))/(1:n)
g <- ggplot(data.frame(x = 1:n, y = means), aes(x = x, y = y))
g <- g + geom_hline(yintercept = 0.5) + geom_line(size = 2)
g <- g + labs(x = "Number of obs", y = "Cumulative mean")
g
```
As coin flips goes to the infinity trials, variablity decreases and converges to the mean


##Central Limit Theorem
Example

##Asymptotics and confidence intervals

####Give a confidence interval for the average height of sons
```{r}
library(UsingR)
data(father.son)
x <- father.son$sheight
(mean(x) + c(-1, 1) * qnorm(0.975) * sd(x)/sqrt(length(x)))/12
```
Example 
You campaign advisor told you that in a random sample of 100 likely voters, 56 intent to vote for you.
    - Can you relax? Do you have this race in the bag
    - Without access to a computer or calculator, how precise this estimate
1/sqrt(100)=0.1 so a back of the envelope calculation gives an approximate 95% interval of (0.46,0.66)
    - Not enough for you to relax,better go do more campaigning!
Rough guidelines,100 for 1 decimal place, 10,000 for 2, 1,000,000 for 3.
```{r}
round(1/sqrt(10^(1:6)),3)
```
####Binomial interval
```{r}
0.56+c(-1,1)*qnorm(0.975)*sqrt(0.56*0.44/100)

binom.test(56,100)$conf.int
```

###Simulation
```{r}
n <- 20 ## n is small
pvals <- seq(0.1, 0.9, by = 0.05)
nosim <- 1000
coverage <- sapply(pvals, function(p) {
    phats <- rbinom(nosim, prob = p, size = n)/n
    ll <- phats - qnorm(0.975) * sqrt(phats * (1 - phats)/n)
    ul <- phats + qnorm(0.975) * sqrt(phats * (1 - phats)/n)
    mean(ll < p & ul > p)
})
library(ggplot2)
g <- ggplot(data.frame(x = 1:17, y = coverage), aes(x = x, y = y))
g <- g + geom_hline(yintercept = 0.5) + geom_line(size = 2)
g <- g + labs(x = "Number of obs", y = "Coverge")
g


```

###What's happening
    - n isn't large enough for the CLT to be applicable for many of the values of p
    - Quick fix, form the interval with
                    (X+2)/(n+4)
    (Add two successes and failures, Agresti/Coull interval)
    
```{r}
n <- 100 ##with large n
pvals <- seq(0.1, 0.9, by = 0.05)
nosim <- 1000
coverage2 <- sapply(pvals, function(p) {    
    phats <- rbinom(nosim, prob = p, size = n)/n    
    ll <- phats - qnorm(0.975) * sqrt(phats * (1 - phats)/n)    
    ul <- phats + qnorm(0.975) * sqrt(phats * (1 - phats)/n)    
    mean(ll < p & ul > p)
})
g <- ggplot(data.frame(x = 1:17, y = coverage2), aes(x = x, y = y))
g <- g + geom_hline(yintercept = 0.5) + geom_line(size = 2)
g <- g + labs(x = "Number of obs", y = "Coverge")
g
```



Look back to the second previous  but with some fix such as adding 2 successes and failure
```{r}
n <- 20
pvals <- seq(0.1, 0.9, by = 0.05)
nosim <- 1000
coverage <- sapply(pvals, function(p) {   
    phats <- (rbinom(nosim, prob = p, size = n) + 2)/(n + 4)    
    ll <- phats - qnorm(0.975) * sqrt(phats * (1 - phats)/n)    
    ul <- phats + qnorm(0.975) * sqrt(phats * (1 - phats)/n)    
    mean(ll < p & ul > p)
})
g <- ggplot(data.frame(x = 1:17, y = coverage), aes(x = x, y = y))
g <- g + geom_hline(yintercept = 0.5) + geom_line(size = 2)
g <- g + labs(x = "Number of obs", y = "Coverge")
g
```


##Poisson Interval
```{r}
x <- 5
t <- 94.32
lambda <- x/t
round(lambda + c(-1, 1) * qnorm(0.975) * sqrt(lambda/t), 3)

poisson.test(x, T = 94.32)$conf
```

####Simulating the poisson coverage rate
```{r}
lambdavals <- seq(0.005, 0.1, by = 0.01)
nosim <- 1000
t <- 100
coverage <- sapply(lambdavals, function(lambda) {
    lhats <- rpois(nosim, lambda = lambda * t)/t
    ll <- lhats - qnorm(0.975) * sqrt(lhats/t)
    ul <- lhats + qnorm(0.975) * sqrt(lhats/t)
    mean(ll < lambda & ul > lambda)
})
g <- ggplot(data.frame(x = 1:10, y = coverage), aes(x = x, y = y))
g <- g + geom_hline(yintercept = 0.5) + geom_line(size = 2)
g <- g + labs(x = "Number of obs", y = "Coverge")
g
```




