---
title: "Data Products  week3 assignment"
author: "Ryu Uezato"
date: "May 11, 2019"
output: ioslides_presentation
---

##Markdwon Presentation & Plotly

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

##Mtcars data correlation
```{r, echo=FALSE}
library(datasets)
data("mtcars")

res = cor(mtcars)
round(res,2)
```

##3D graphics
```{r, echo=FALSE, warning=FALSE, message=FALSE}
require(plotly)
data = as.data.frame(cbind(mtcars$mpg, mtcars$cyl, mtcars$wt))
colnames(data) = c("mpg", "cly", "wt") ; data$cly = as.factor(data$cly)
p <- plot_ly(data, x = ~wt, y = ~cly, z = ~mpg, color = ~cly, colors = c('#BF382A', '#0C4B8E')) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Weight'),
                     yaxis = list(title = 'the number of clynder'),
                     zaxis = list(title = 'Miles per Galaon')))
p
```


##Regression Model
```{r, echo=FALSE}
fit = lm(mpg ~ cly + wt, data = data)

fit
```

Based on the regression on weight and the number of clynder, as the more number of cylinder a car has,  the lower fuel consumption a car has. Futhermore, as a cars's weight is higher, a car's ability to run distance will be lesser and lesser.
